\documentclass[a4paper]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{paralist}
\usepackage{epstopdf}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyvrb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{paralist}
\usepackage[svgname]{xcolor}
\usepackage{enumerate}
\usepackage{array}
\usepackage{times}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{comment}
\usepackage{environ}
\usepackage{times}
\usepackage{textcomp}
\usepackage{caption}


\urlstyle{rm}

\setlength\parindent{0pt} % Removes all indentation from paragraphs
\theoremstyle{definition}
\newtheorem{definition}{Definition}[]
\newtheorem{conjecture}{Conjecture}[]
\newtheorem{example}{Example}[]
\newtheorem{theorem}{Theorem}[]
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Nat}{\mathbb{N}}
\newcommand{\br}[1]{\{#1\}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\renewcommand{\qedsymbol}{$\blacksquare$}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}

\newcommand{\vc}[1]{\boldsymbol{#1}}
\newcommand{\xv}{\vc{x}}
\newcommand{\Sigmav}{\vc{\Sigma}}
\newcommand{\alphav}{\vc{\alpha}}
\newcommand{\muv}{\vc{\mu}}

\newcommand{\red}[1]{\textcolor{red}{#1}}

\def\x{\mathbf x}
\def\y{\mathbf y}
\def\w{\mathbf w}
\def\v{\mathbf v}
\def\E{\mathbb E}
\def\V{\mathbb V}

% TO SHOW SOLUTIONS, include following (else comment out):
\newenvironment{soln}{
    \leavevmode\color{blue}\ignorespaces
}{}


\hypersetup{
%    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\geometry{
  top=1in,            % <-- you want to adjust this
  inner=1in,
  outer=1in,
  bottom=1in,
  headheight=3em,       % <-- and this
  headsep=2em,          % <-- and this
  footskip=3em,
}


\pagestyle{fancyplain}
\lhead{\fancyplain{}{Homework 2: Written Exercise Part}}
\rhead{\fancyplain{}{CS 760 Machine Learning}}
\cfoot{\thepage}

\title{\textsc{Homework 2: \\ Written Exercise Part}} % Title

%\newcommand{\outDate}{Aug. 31, 2016}
%\newcommand{\dueDate}{5:30 pm, Sep. 7, 2016}


%%% NOTE:  Replace 'NAME HERE' etc., and delete any "\red{}" wrappers (so it won't show up as red)

%\author{
%\red{$>>$NAME HERE$<<$} \\
%\red{$>>$ID HERE$<<$}\\
%} 

\date{}

\begin{document}

\maketitle 


\section{Information Theory [25/4 pts]}
Suppose $X, Y$ are two random variables taking values in a discrete finite set $V$. Let $H(Y)$ denote the entropy of $Y$, and let $H(Y|X)$ denote the conditional entropy of $Y$ conditioned on $X$. Prove that if $X, Y$ are independent, then $H(Y)=H(Y|X)$.

\begin{soln}  Solution goes here. \end{soln}


\section{Standardizing Numeric Features [25/4 pts]}
Standardize the data set with four points in 2 dimension: $(7, 7), (3, 7), (3, 3), (7, 3)$.

\begin{soln}  Solution goes here. \end{soln}


\section{$k$-Nearest Neighbors [25/4 pts]}
Consider the training data set $x_1 = (7, 7), y_1 = 0; x_2 =  (3, 7), y_2 = 1; x_3 = (3, 3), y_3 = 1; x_4 = (7, 3), y_4 = 2$. Suppose the Manhattan distance is used. What is the label for $x = (0, 0)$ in the following settings? Show the calculation steps.
\begin{enumerate}
	\item $1$-nearest neighbors.
	\item $3$-nearest neighbors.
	\item $3$-nearest neighbors, distance weighted. The weight for the $i$-th neighbor $z$ is $1/d(x, z)^2$.
\end{enumerate}

\begin{soln}  Solution goes here. \end{soln}


\section{Performance Measurements [25/4 pts]}
Consider the following confusion matrix for 2 classes.

\begin{table}[H]
	\centering
		\begin{tabular}{ccc}
			& actual positive & actual negative \\
			\hline
			predict positive & 76 & 18\\
			\hline
			predict negative & 24 & 82\\
			\hline
		\end{tabular}
\end{table}

Compute the accuracy, error, true positive rate, false positive rate, precision, and recall. 

\begin{soln}  Solution goes here. \end{soln}


\bibliographystyle{apalike}


%----------------------------------------------------------------------------------------


\end{document}
